Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-11-20 ms/spaceness.tex
.

One facet of spatial variation that we did not address in this study is the confounding of dispersal and population density implicit in the definition of Wright's neighborhood size. Our simulations were run under constant densities, but \cite{guindon2016demographic} and \citet{Ringbauer2017} have shown that these parameters are identifiable under some continuous models. Similarly, though the scaling effects of dispersal we show in Figure \ref{fig:sumstats} should occur in populations of any total size, other aspects such as the number of segregating sites are also likely affected by the total landscape size (and so total census $N$)\llabel{landscapesizecaveat}. Much additional work remains to be done to better understand how these parameters interact to shape genetic variation in continuous space, which we leave to future studies.

>>>>

One facet of spatial variation that we did not address in this study is the confounding of dispersal and population density implicit in the definition of Wright's neighborhood size. Our simulations were run under constant densities, but \cite{guindon2016demographic} and \citet{Ringbauer2017} \revpoint{3}{8}
have shown that these parameters are identifiable under some continuous models. Similarly, though the scaling effects of dispersal we show in Figure \ref{fig:sumstats} should occur in populations of any total size, other aspects such as the number of segregating sites are also likely affected by the total landscape size (and so total census $N$)\llabel{landscapesizecaveat}. Much additional work remains to be done to better understand how these parameters interact to shape genetic variation in continuous space, which we leave to future studies.
